Spin canonical rings of log stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex

\begin{rem}
\label{rem:gen-at-most-three}
In the case that $M(\Gamma)$ has some odd weight modular form, it in fact has an odd weight modular form in weight $3$. This holds in the case that the genus $g \geq 2$ because $\deg \lfloor 3L \rfloor > 2g-1,$ so by Riemann--Roch, $\dim_k H^0(\sx,3L) > 0,$ implying there must be some generator in weight $1$ or $3$. The case that $M(\Gamma)$ has a generator in degree 1 or 3 when $g(X) = 0$ or $1$ follows from the fact that it has such a generator in the base cases given in Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}. Hence, the bound on the degree of generators and relations in the case that $M(\Gamma)$ has some odd weight modular form, given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
\end{rem}

\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0). Further, if $L_X$ is effective, then generation will be in weight at most 3.}
\begin{example}
\label{eg:congruence-bounds}
Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the action of $\Gamma$ can only have points with stabilizer order 2 and 3. Furthermore, if $\Gamma$ has some odd weight modular form, then it must have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is generated in degree at most $5$ with a relation in degree at most $12$. Furthermore, if the coarse space associated $\Gamma$ does not have .
\end{example}

\begin{rem}
\label{rem:factor-two}
In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ and relation
bound of $12 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $2\cdot \max(3,e_1, \ldots, e_r)$ and $4 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively. Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two, because our grading convention on $\bigoplus_k M_k(\Gamma)$ differs from that of Voight and Zureick-Brown by a factor of 2.
\end{rem}

>>>>

\begin{rem}
\label{rem:gen-at-most-three}
If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$. When $g \geq 2$, we see that this is true because $\dim_k H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$. When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases} so there is an odd weight modular form in weight $3$ in general. A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
\end{rem}

\begin{example}
\label{eg:congruence-bounds}
Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since 
the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the 
action of $\Gamma$ can only have points with stabilizer order 2 and 3. 
Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
generated in degree at most $5$ with relations in degree at most $12$. 
Furthermore, if the coarse space associated $\Gamma$ does not have, 
$(0;3,3,3,3;0),$ there are relations in degree at most $10$, as follows 
from the list of exceptional cases in Tables ~\ref{table:genus-0-exceptional-cases} and ~\ref{table:genus-0-exceptional}.
\end{example}

\begin{rem}
\label{rem:factor-two}
In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ and relation
bound of $12 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $2\cdot \max(3,e_1, \ldots, e_r)$ and $4 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively. Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two. Our grading convention for log spin canonical rings uses weight $k$ for the degree whereas Voight and Zureick-Brown $d = 2k$ for degree.
\end{rem}
